Develop atlantisom wrappers

### 2020-01-17 WrapperDevelopment.Rmd
test wrappers with changed config files

```{r exinit}

@@

```{r exsp}

@@

```{r exindex}

@@

@@

Usage:
```{r compex}

@@

>>>>

```{r exinit, eval=FALSE}

@@

```{r exsp, eval=FALSE}

@@

```{r exindex, eval=FALSE}

@@

ToDo: write the atlantisom function sample_ages to subset the age comp here, that way there will be way more lengths than ages, similar to most real world sampling.

@@

Usage:
```{r compex, eval=FALSE}

@@

Test these with updated length-weight parameters for CCA sardines:

I updated CalCurrentV3_Biol.prm with new sardine length-weight parameters from Isaac

>On the basis of the last sardine stock assessment that seems to have estimated growth, 
http://www.pcouncil.org/wp-content/uploads/2014_CPS_SAFE_Sardine_assessment_Appendix_C.pdf 
>
>I say length-weight A and B params,  for W = A*(L^B)
>
>should be A= 0.0075242
>and B = 3.2332
>
>where weight is in grams
>and length is in CM.

and renamed it CalCurrentV3_Biol_sardLWcorrection.prm

Config files for this extraction should match previous sardine survey and fishery:

CC3Config_sardLWcorr.R
sardinesurvey.R
sardinefishery.R

```{r full-test}

library(here)

CC3om <- om_init(here("config/CC3config_sardLWcorr.R"))

CC3om_sard_ind <- om_index(usersurvey = here("config/sardinesurvey.R"), 
                           userfishery = here("config/sardinefishery.R"),
                           omlist_ss = CC3om_sardine, 
                           n_reps = 1, 
                           save = TRUE)

CC3om_sard_comp <- om_comps(usersurvey = here("config/sardinesurvey.R"), 
                           userfishery = here("config/sardinefishery.R"),
                           omlist_ss = CC3om_sardine, 
                           n_reps = 1, 
                           save = TRUE)
